TEMPERATURES AND METALLICITIES FOR 10,000 M DWARFS\\ IN THE \apogee\ SURVEY

### 2018-08-14 paper/draft.tex
typo
add to cmd caption

We note that surface gravity is not inclided as a training label. The reason for this is that for main-sequence M dwarfs, the parameter is almost entirely redundant with metallicity. Unlike their higher-mass counterparts, M dwarf properties do not change measurably over the age of the Universe. Hence perfect knowledge of abundances and \teff\ for an M dwarf should uniquely determine its position its surface gravity, position on a color-magnitude diagram, and overall luminosity. While we only had [Fe/H] for the training sample, for the uncertainties considered here, lack of information about [$\alpha$/Fe] or specific abundances will only be important for extreme cases (e.g., Carbon stars). Highly active stars

%%AWM: Feel free to edit this for clarity. Let me know if anything makes no sense. 
%We note that rotational velocity (vsini) is not a parameter are not included as training labels because that would be hard... also it's probably not needed... I'll let someone else write that. -AWM
%\color{gcolor}{}\color{black}

@@

\begin{figure}[ht]
\gridline{\fig{figures/safe_selection_teff.png}{0.5\textwidth}{}
          \fig{figures/safe_selection_feh.png}{0.5\textwidth}{}}
\gridline{\fig{figures/safe_selection_spt.png}{0.5\textwidth}{}}
\caption{Final sample selection with 10,311 M dwarfs based on criteria described in Section \ref{subsec:test_selection}. \label{fig:safe_selection}}
\end{figure}

>>>>

We note that surface gravity is not inclided as a training label. The reason for this is that for main-sequence M dwarfs, the parameter is almost entirely redundant with metallicity. Unlike their higher-mass counterparts, M dwarf properties do not change measurably over the age of the Universe. Hence perfect knowledge of abundances and \teff\ for an M dwarf should uniquely determine its position its surface gravity, position on a color-magnitude diagram, and overall luminosity. While we only had [Fe/H] for the training sample, for the uncertainties considered here, lack of information about [$\alpha$/Fe] or specific abundances will only be important for extreme cases (e.g., Carbon stars).

%%AWM: Feel free to edit this for clarity. Let me know if anything makes no sense.

%We note that rotational velocity (vsini) is not a parameter are not included as training labels because that would be hard... also it's probably not needed... I'll let someone else write that. -AWM
%\color{gcolor}{}\color{black}

@@

\begin{figure}[ht]
\gridline{\fig{figures/safe_selection_teff.png}{0.5\textwidth}{}
          \fig{figures/safe_selection_feh.png}{0.5\textwidth}{}}
\gridline{\fig{figures/safe_selection_spt.png}{0.5\textwidth}{}}
\caption{Final sample selection with 10,311 M dwarfs based on criteria described in Section \ref{subsec:test_selection}; temperature gradient increases with decreasing color, spectral subtype increases with increasing color, and metallicity gradient increases with increasing absolute magnitude as expected. Deviations from these gradients seen at the upper slice of the main sequence is due to binaries. \label{fig:safe_selection}}
\end{figure}
